---
title: "Reproducible example"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, error = FALSE)
library(tidyverse)
```

## Summary

In this repo we will examine the ForRichness dataset and the Richness dataset

```{r}
Richness <- read_csv("Richness.csv")

ForRichness <- read_csv("ForRichness.csv")

FinalDataset <- full_join(Richness, ForRichness)
```

## Just an example of inlinde code

In our dataset, the median richness for all of our sites is `r median(FinalDataset$Richness)` species of plants, from the year `r min(FinalDataset$year)` to the year `r max(FinalDataset$year)` for `r prettyNum(length(unique(FinalDataset$ID)), big.mark = ".", decimal.mark = ",")` sites


## Example of one table

```{r}
Summary <- FinalDataset %>% 
  dplyr::filter(!is.na(MajorHab)) %>% 
  group_by(MajorHab) %>% 
  summarise(MedianRichness = mean(Richness), MaxRichness = max(Richness), MinRichness = min(Richness))
knitr::kable(Summary, digits = 2, caption = "Summary of number of species according to major habitats")
```

